Minimizing post-shock forecasting error through aggregation of outside information

### 2021-01-22 Revision/manuscript.tex
finished round of revisions

We also consider the inverse-variance weighted estimator 
in practical settings where the $T_i$s and $T_i^*$s vary greatly across $i=2, \ldots, n+1$. 
The inverse-variance weighted estimator is defined as 
\begin{align*}
  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{M}_i'\mbf{M}_i)_{22}^{-1},
\end{align*}
where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, $\hat{\sigma}_i$ is the residual standard error from OLS estimation, and $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation is required and the numerator and denominator terms are dependent in general. However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in practical settings, especially when the $T^*_i$s very considerably. We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of $\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation (see Section \ref{simulation}).

@@

In this section we provide justification for our methods based on Monte Carlo simulation. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}. The parameter setup of our simulations is detailed as follows: 
\begin{align*}
  \phi_i &\simiid U(0,1),	\\
  \delta_i &\simiid  \normal{1}{0.5^2}, \\
  \theta_i &\simiid \normal{0}{1}, \\
  \alpha_i &\simiid \normal{\mu_\alpha}{\sigma_{\alpha}^2}, \\
  T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
  T_i^* &\simiid \red{U\{p+4, T_i-1\}}, \\
  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2},
\end{align*}
where the $[\cdot]$ operation in the generation of the $T_i$'s corresponds to rounding the input to the nearest integer, \red{$U(a,b)$, $U\{a,b\}$, and $\mrm{Gamma}(c,d)$  stands for a random variable from continuous uniform distribution on the closed interval from $a$ to $b$, discrete uniform distribution on the set of integers from $a$ and $b$, and Gamma distribution with shape parameter $c$ and scale parameter $d$, respectively}. The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Additionally, we generated all of the entries of the covariate vectors to be realizations from a $\text{Gamma}(1,2)$ distribution.

@@

In this section, we discuss two real data examples of post-shock prediction. Section \ref{forecasting} discusses the prediction of Conoco Phillips stock occurring on March 9th, 2020. This shock relates to an oil price war and the COVID-19 pandemic. Section \ref{apple} applies our proposed method to the forecasting of Apple stock prices after releasing the latest version of their MacBook product. These examples provide empirical illustration of our methodology in settings where the shock is, respectively, unprecedented and with precedent.  \textcolor{red}{Generalizations of our method are discussed as well. Section \ref{forecasting} allows the shock effect to be decomposed into separable estimable parts,  multiple shock effects to be nested in a time series, and different models for the response and the shock effects. Section \ref{apple} extends the forecasting adjustment at $T_1^*+1$ to $T_1^*+2$, and considers  a different model of the time series of interest  to that of   donor pool. In terms of the results, the adjusted forecast in Section \ref{forecasting} performs much better than the unadjusted original forecast, and the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.}

@@

\begin{enumerate}
\item[(1)] {\bf Selection of model}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.  For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$. The model of $\alpha_i$ incorporates lagged daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX). The model for $y_{i,t}$ disregards VIX. This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
\item[(3)] {\bf Construction of donor pool}. Our donor pool consists of Conoco Phillips shock effects observed in the past. We consider shock effects which occurred on March 15, 2008, several days in September, 2008, and November 27, 2014. The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession. In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}. These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Macbook in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}. The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}. 
\end{enumerate}

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well. Our estimation framework misses the yet to be observed pot-shock response, however they perform much better than unadjusted forecasts that do not account for shock effects. The unadjusted forecast misses the post-shock response by 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively.

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since Macbook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of Macbooks account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. after the release of the latest MacBook on November, 10th, 2020. \textcolor{red}{From knowledge from our donor pool (see  (3) Construction of donor pool below), we observe that it takes two days for the shock effect to take hold.} Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020, \red{when we conjecture that the time series of interest would experience a shock}. \red{We collect our data through   \texttt{quantmod} package \citep{ryan2017quantmod} in R.} The detailed considerations of our analysis are outlined as below.

\begin{enumerate}[label = (\arabic*)]
  \item \red{\textbf{Selection of model.}}  We use an AR(1) model to forecast the stock price of Apple Inc. All the estimates will be adjusted for inflation.  We consider $D_{i, t} = I(t = T_i^*+2)$. By observing  the data, we found a large shock effect on October 10th, 2020, two days before the release of iPhone 12, iPhone 12 Pro, MagSafe accessories, and HomePod mini. Denote this date by $T_{1,\#}$, and the shock effect by $\beta$. We account for this shock effect that is not of our interest in the model by setting 
  \begin{align*}
    y_{1,t} &= \eta_i + \alpha_1 D_{1,t} +\phi_1y_{1, t-1}+\theta_1'\mathbf{x}_{1,t} + \beta I(t = T_{1,\#}) + \varepsilon_{i,t}.
  \end{align*}
  The model for $y_{i,t}$ is the same as in Section \ref{modelsetup} for $i = 2, \ldots, n+1$.   The model for the shock effect is
  \begin{align*}
    \alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{i,T_i^*+2}  + \tilde{\varepsilon}_{i,t}.
  \end{align*}
  Then, the weighting schemes introduced in Section \ref{constructionofestimators} will use  $\{\mathbf{x}_{i,T_i^*+2} \colon i = 1, \ldots, n+1\}$ for computing $\mathbf{W}^*$, where $\mathbf{x}_{1, T_1^*+2}$ will require prediction as detailed in (2) Selection of covariates. We used mean squared error for the response in the training data to select an appropriate time length out of 20, 25, 30, and 50 trading days. As a result, we consider 25 trading days data for the time series of interest and time series in the donor pool. 
  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. We then predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date in the middle of \red{25} trading days for 2017, 2018, and 2019.  The specific shock-effect dates are June 6th, 2017, October 30th, 2018, and June 3rd, 2019, respectively. We only include the last three Macbook releases in our donor pool because \red{we conjecture that} those releases are similar to the current release in the sense that Apple inc. has only updated the hardware of the computer without much redesign in these releases \citep{apple2017, apple2018, apple2019}; \red{and it is indeed consistent \citep{apple2020}}.  %The new MacBook series is built with M1 chip invented by Apple inc. instead of chips by Intel inc. that were used in past years, and their CPU speed improves significantly \citep{apple2020}. 
\end{enumerate}

The covariates and response of time series in the donor pool are adjusted for inflation. The estimated shock effects $\alpha_i$ are $0.686, 1.688, 1.393$ for $i = 2, 3, 4$, respectively. We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$. As a result, we compute $\mathbf{W}^* = (0.712, 0.000, 0.288)$ and $
  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 2.422$. It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects. The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.256$, $\hat{\alpha}_{\rm wadj}=0.889$, and $\hat{\alpha}_{\rm IVW} = 0.951$. The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.245$, $0.134$, and $0.133$, respectively. Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk. As we can see from Figure \ref{Fig3}, the post-shock forecasts perform well. The unadjusted forecast misses the post-shock by 0.799 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.457, 0.090, and 0.152 dollars, respectively. \red{It appears that covariates weighting with $\hat{\alpha}_{\rm wadj}$ is more successful. It is possible that $\mc{M}_2$ is a good fit for the data. Note  that the 1-ahead forecast error for $y_{1, T_1^*+1}$ and the covariates contribute to some of the forecast risk.}

@@

We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings. The model, under which we verify these claims, is a simple AR(1) model. Similar results can be obtained for more general models \red{whose parameter can be estimated unbiasedly}. %such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models. 
Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent. As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock. But we note that consistency estimates from LOOCV may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.

Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its second moments exist. The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.  Additionally, $\alpha_i$ can be heteroskedastic; i.e.,  they can have different variances. In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply. We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts. An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis. Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.

We can extend the proposed nowcasting to forecast  the response for $m$ periods, where $m\geq 2$. Without loss of generality, we assume $m = 2$. There are two cases. First, suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. Second, assume that the time series under study will experience a shock at $T_1^* + 2$, say $\alpha_1^{(2)}$.  Under our framework, users may want to construct another set of donor pool with time series that experience shock similar to  $\alpha_1^{(2)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(2)}$.  The forecast at $t = T_1^* + 2$ is
\begin{align*}
  \hat{y}^2_{1, T_1^*+2}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +2} + \hat{\alpha}_1^{(2)},
\end{align*} 
where $\hat{y}_{1, T_1^* + 1}^2$ is defined as in Section \ref{forecast}. These two cases can be generalized to  forecasting $m\geq 2$ more periods. The scenarios for forecasting in AR($p$), or other general models are analogous.

In the setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$. The methodology can be extended to more general timing scenarios. Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool. \red{The Apple example illustrates the case when $d = 2$ with predicted covariates, where the prediction error for covariates and response can contribute to the post-shock forecast risk.}

>>>>

We also consider the inverse-variance weighted estimator 
in practical settings where the $T_i$s and $T_i^*$s vary greatly across $i=2, \ldots, n+1$. 
The inverse-variance weighted estimator is defined as 
\begin{align*}
  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{M}_i'\mbf{M}_i)_{22}^{-1},
\end{align*}
where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, $\hat{\sigma}_i$ is the residual standard error from OLS estimation, and $\mbf{M}_i$ is the design matrix for OLS with respect to time series for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation is required and the numerator and denominator terms are dependent in general. However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in practical settings, especially when the $T^*_i$s vary considerably. We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of $\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation (see Section \ref{simulation}).

@@

In this section we provide justification for our methods based on Monte Carlo simulation. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=25$ and $\mu_{\alpha}=2$, where $p = 25$ is set to satisfy conditions in Proposition \ref{uniqueness}. The parameter setup of our simulations is detailed as follows: 
\begin{align*}
  \phi_i &\simiid U(0,1),	\\
  \delta_i &\simiid  \normal{1}{0.5^2}, \\
  \theta_i &\simiid \normal{0}{1}, \\
  \alpha_i &\simiid \normal{\mu_\alpha}{\sigma_{\alpha}^2}, \\
  T_i &\simiid \min\left(90, [\text{Gamma}(15,10)]\right), \\
  T_i^* &\simiid U\{p+4, T_i-1\}, \\
  \varepsilon_{i,t} &\simiid \normal{0}{\sigma^2},
\end{align*}
where the $[\cdot]$ operation in the generation of the $T_i$'s corresponds to rounding the input to the nearest integer, $U(a,b)$, $U\{a,b\}$, and $\mrm{Gamma}(c,d)$, respectively,  denotes the continuous uniform distribution on the closed interval from $a$ to $b$, discrete uniform distribution on the set of integers from $a$ and $b$, and Gamma distribution with shape parameter $c$ and scale parameter $d$, respectively. The choices of $T_i$ and $T_i^*$ are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is  designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Additionally, we generated all of the entries of the covariate vectors to be realizations from a $\text{Gamma}(1,2)$ distribution.

@@

In this section, we discuss two real data examples of post-shock prediction. Section \ref{forecasting} discusses the prediction of Conoco Phillips stock occurring on March 9th, 2020. This shock relates to an oil price war and the COVID-19 pandemic. Section \ref{apple} applies our proposed method to the forecasting of Apple stock prices after releasing the latest version of their MacBook product. These examples provide empirical illustration of our methodology in settings where the shock has, respectively, unprecedented and precedented origins.  %\textcolor{red}{Generalizations of our method are discussed as well. Section \ref{forecasting} allows the shock effect to be decomposed into separable estimable parts,  multiple shock effects to be nested in a time series, and different models for the response and the shock effects. Section \ref{apple} extends the forecasting adjustment at $T_1^*+1$ to $T_1^*+2$, and considers  a different model of the time series of interest  to that of   donor pool. In terms of the results, the adjusted forecast in Section \ref{forecasting} performs much better than the unadjusted original forecast, and the adjusted forecast in Section \ref{apple} is very close to the response after shock as reasonably expected.}

@@

\begin{enumerate}
\item[(1)] {\bf Selection of model}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.  For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$. The model of $\alpha_i$ incorporates lagged daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX). The model for $y_{i,t}$ disregards VIX. This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
\item[(3)] {\bf Construction of donor pool}. Our donor pool consists of Conoco Phillips shock effects observed in the past. We consider shock effects which occurred on March 15, 2008, several days in September, 2008, and November 27, 2014. The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession. In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}. These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie MacBook in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}. The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}. 
\end{enumerate}

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well. Our estimation framework misses the yet to be observed post-shock response. However, they perform much better than unadjusted forecasts that do not account for shock effects. The unadjusted forecast misses the post-shock response by 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively.

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since MacBook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of MacBooks account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. after the release of the latest MacBook on November, 10th, 2020. Our donor pool suggests that it takes two days for the shock effect to take hold. Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020. Our data is collected using the \texttt{quantmod} package \citep{ryan2017quantmod} in R. The detailed considerations of our analysis are outlined as below:

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc. All the estimates will be adjusted for inflation.  We consider $D_{i, t} = I(t = T_i^*+2)$. By observing  the data, we found a large shock effect on October 10th, 2020, two days before the release of iPhone 12, iPhone 12 Pro, MagSafe accessories, and HomePod mini. Denote this date by $T_{1,\#}$, and the shock effect by $\beta$. We account for this shock effect that is not of our interest in the model by setting 
  \begin{align*}
    y_{1,t} &= \eta_i + \alpha_1 D_{1,t} +\phi_1y_{1, t-1}+\theta_1'\mathbf{x}_{1,t} + \beta I(t = T_{1,\#}) + \varepsilon_{i,t}.
  \end{align*}
  The model for the shock effect is
  \begin{align*}
    \alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{i,T_i^*+2}  + \tilde{\varepsilon}_{i,t}.
  \end{align*}
  Then, the weighting schemes introduced in Section \ref{constructionofestimators} will use  $\{\mathbf{x}_{i,T_i^*+2} \colon i = 1, \ldots, n+1\}$ for computing $\mathbf{W}^*$, where $\mathbf{x}_{1, T_1^*+2}$ will require prediction as detailed in (2) Selection of covariates. We used mean squared error for the response in the training data to select an appropriate time length out of 20, 25, 30, and 50 trading days. As a result, we consider 25 trading days data for the time series of interest and time series in the donor pool. 
  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. We then predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date in the middle of 25 trading days for 2017, 2018, and 2019.  The specific shock-effect dates are June 6th, 2017, October 30th, 2018, and June 3rd, 2019, respectively. We only include the last three MacBook releases in our donor pool. This is because these releases are similar to the current release, Apple inc. has only updated the hardware of the computer without much redesign of the MacBook \citep{apple2017, apple2018, apple2019}. The same is the case with the lastest MacBook release \citep{apple2020}.  %The new MacBook series is built with M1 chip invented by Apple inc. instead of chips by Intel inc. that were used in past years, and their CPU speed improves significantly \citep{apple2020}. 
\end{enumerate}

The covariates and response of time series in the donor pool are adjusted for inflation. The estimated shock effects $\alpha_i$ are $0.686, 1.688, 1.393$ for $i = 2, 3, 4$, respectively. We centered and scaled the covariates in weights computation but not in the model of $y_{i,t}$. As a result, we compute $\mathbf{W}^* = (0.712, 0.000, 0.288)$ and $
  \|\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\|_2 = 2.422$. It appears that  the shock effect of interest is similar to 2017 and 2019 shock effects. The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}= 1.256$, $\hat{\alpha}_{\rm wadj}=0.889$, and $\hat{\alpha}_{\rm IVW} = 0.951$. The bootstrap estimates variances for variances for $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$,  and $\hat{\alpha}_{\rm IVW}$ are $0.245$, $0.134$, and $0.133$, respectively. Our risk-reduction propositions yield that those shock-effect estimators reduce the post-shock forecast risk. As we can see from Figure \ref{Fig3}, the post-shock forecasts perform well. The unadjusted forecast misses the post-shock by 0.799 dollars, while the use of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ only miss by 0.457, 0.090, and 0.152 dollars, respectively. In this example, covariates weighting to construct $\hat{\alpha}_{\rm wadj}$ is more successful than the other techniques, it is possible that model $\mc{M}_2$ fits this data well. Note  that the 1-ahead forecast error for $y_{1, T_1^*+1}$ and the covariates contribute to some of the forecast risk.

@@

We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings. The model, under which we verify these claims, is a simple AR(1) model. Similar results can be obtained for more general models whose parameters can be estimated unbiasedly. %such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models. 
Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent. As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock. But we note that consistency estimates from LOOCV may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.

Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its second moments exist. The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.  Additionally, $\alpha_i$ can be heteroskedastic; i.e.,  they can have different variances. In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply. We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts. An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis. Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.

In our setup, we assume that at $t=T_1^*$, the user knows there will be a shock at $t=T_1^*+1$. The methodology can be amended to accommodate different timing scenarios. Suppose that we know at $T_1^*$ that a shock is about to occur at $T_1^* + d$ for $d\geq 1$ and $d\in \mathbb{N}$, and that we have information about the future covariates for $t = T_1^* +1 , \ldots, T_1^* + d$. We can make a scalar adjustment for original forecast at $T_1^*+d$ using shock-effect estimator constructed from donor pool. The Apple example illustrates the case when $d = 2$ with predicted covariates, where the prediction error for covariates and response can contribute to the post-shock forecast risk.

We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead. %We present one possible generalization under the specification that $m = 2$. 
In this setting, there are two cases. In the first case, we suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. In the second case, we assume that the time series under study will experience an additional additive shock at $T_1^* + m$, say $\alpha_1^{(m)}$. Users now construct the donor pool to consist of time series that experience shocks similar to  $\alpha_1^{(m)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(m)}$.  The adjusted forecast at $t = T_1^* + m$ is
$
  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}.
$
